\documentclass{article}
\usepackage{amsthm}

\newtheorem{definition}{Definition}[section]
\newtheorem{axiom}{Axiom}[section]

\begin{document}

\section{Forecast}
\begin{definition}[market strength forecast]
    \label{msf}
\end{definition}
\begin{definition}[market risk forecast]
    \label{mrf}
\end{definition}
\begin{definition}[capital\% put into a trade]
    \label{cpit}
\end{definition}
\begin{axiom}
    Definition~\ref{cpit} shoud be larger if Definition~\ref{msf} is stronger
\end{axiom}
\begin{axiom}
    Definition~\ref{cpit} shoud be smaller if Definition~\ref{mrf} is larger
\end{axiom}


focus at now, why?
1. entertaining
2. understanding
3. creating
what about future? I really don't care
but there is consequence

what is the consequence of my random playing?
What is my Toy?
    36 time series
        price
        forecast
        indicator

 How to Flirt with it? how to have fun with adult toy? Trust Your Process.
    do others seem to be having fun? can I feel their fun? empirically, yes.
        need to stress this impression
        recording their fun
        1. portfolio level, diversification, picking market, leverage
        2. other fields
            Exploratary Data Analysis?
            Financial-Time-Series-Analyzing?
            Natural-Language-Processing?
            Singal-Processing?
        3. myself
            at beginning fear of future
            ...
            ...information accumulating
            ...
            at end knowing past

forecast into future +  = money?
human psychological construct

model specification?
model testing? maximum likelihood

\end{document}